ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/figure_p.tex
reworked figure caption

    \subfigure[aligned MHC pangenome]{
      \includegraphics[width=.48\textwidth]{fig/mhc-align.eps}
      \label{fig:1a}
    }
    \vspace{-11pt}
    % \newline
    \subfigure[consensus MHC pangenome]{
      \includegraphics[width=.48\textwidth]{fig/mhc-pangenome.eps}
      \label{fig:1b}
    }
    \caption{Examples of output generated by \odgi\ visualizing the
      Major Histocompatibility Complex (MHC) \textit{locus}. (a)
      projection of full MHC of eight haploid phased human genome
      assemblies, plus the chm13 cell line and GRCh38 reference
      genomes as supplied by the human reference pangenome
      consortium\citep{RPC} by \cmd{odgi build+sort+viz}. The coloured
      bars represent the linearized paths --- representing individuals
      --- as a zoomed out multi-sequence alignment. The black lines at
      the bottom represent the graph topology. (b) consensus
      representation of the graph of the same MHC assemblies showing
      variations larger than $100$ base pairs created by \cmd{odgi
        build}. The gene label coordinates were super imposed by
      \cmd{odgi position} from GRCh38. Figure genrated by the Bandage
      tool\citep{26099265} }
    \label{fig:1}
  % \end{center}
  \end{minipage}
\end{figure*}

>>>>

        \subfigure[aligned MHC pangenome]{
            \includegraphics[width=.48\textwidth]{fig/mhc-align.eps}
            \label{fig:1a}
        }
        \vspace{-11pt}
        % \newline
        \subfigure[consensus MHC pangenome]{
            \includegraphics[width=.48\textwidth]{fig/mhc-pangenome.eps}
            \label{fig:1b}
        }
        \caption{Visualizing the Major Histocompatibility Complex (MHC) \textit{locus}.
            (a) projection of full MHC \textit{locus} of eight haploid phased human genome
            assemblies, plus the chm13 cell line and GRCh38 reference genomes, as supplied by the
            Human Reference Pangenome Consortium\citep{HRPC}, created by \cmd{odgi build+sort+viz}. The coloured
            bars represent the linearized paths, representing contigs, as a zoomed out multi-sequence
            alignment. The black lines at the bottom represent the graph topology.
            (b) consensus graph representation of the same assemblies showing variations larger than $100$ base pairs.
            The gene label coordinates were super imposed by using \cmd{odgi position} from GRCh38.
            Figure generated by the Bandage tool\citep{26099265}.
        }
        \label{fig:1}
        % \end{center}
    \end{minipage}
\end{figure*}
